\documentclass{report} 
\title{Enderton's Elements of Set Theory}
\date{Started 1st May 2026}
\author{Malcolm}
\usepackage{amsmath} %import math
\usepackage{mathtools} %more math
\usepackage{amssymb} %for QED symbol
\usepackage{amsthm} %
\usepackage{mathrsfs} %
\usepackage{bm}%bold math
\usepackage{graphicx} %import imaging

\graphicspath{{./images/}} %set imaging path

\newtheorem{theo}{Theorem}[chapter]
\newtheorem{theorem}[theo]{Theorem}
\newtheorem{lemma}[theo]{Lemma}
\newtheorem{definition}[theo]{Definition}


\begin{document}
\maketitle

\tableofcontents

\chapter{Axioms and Operations}
\section{First Axioms}
\textit{Extensionality axiom}\\
If two sets have the exact same members, then they are equal:
\begin{equation*}
\forall A\forall B[\forall x(x\in A\leftrightarrow x\in B)\to A=B]
\end{equation*}
(The nested implication is not an equivalence because the other direction is already true. Declaring it would be redundant.)\\
\vspace{1mm}\\
\textit{Empty set axiom}\\
There is a set having no members:
\begin{equation*}
\exists B\forall x(x\notin B)
\end{equation*}
\textit{Pairing axiom}\\
For any sets $u$ and $v$, there is a set having as members just $u$ and $v$:
\begin{equation*}
\forall u\forall v\exists B\forall x(x\in B\leftrightarrow x=u\text{ or }x=v)
\end{equation*}
\textit{Union axiom, Preliminary form}\\
For any sets $a$ and $b$, there is a set whose members are those sets belonging either to $a$ or to $b$ (or both):
\begin{equation*}
\forall a\forall b\exists B\forall x(x\in B\leftrightarrow x\in a\text{ or }x\in b)
\end{equation*}
(next page)\newpage
\noindent\textit{Power set axiom}\\
For any set $a$, there is a set whose members are exactly the subsets of $a$:
\begin{equation*}
\forall a\exists B\forall x(x\in B\leftrightarrow x\subseteq a)
\end{equation*}
We can rewrite $x\subseteq a$ in terms of the definition of $\subseteq$:
\begin{equation*}
\forall t(t\in x\to t\in a)
\end{equation*}
This list will be further expanded later to include
\begin{itemize}
\item Subset axioms
\item Replacement axioms
\item Infinity axiom
\item Regularity axiom
\item Choice axiom
\end{itemize}
The union axiom will be also be restated in a stronger form.
\newpage

\subsection{Definitions}
\begin{definition}
$\emptyset$ is the set having no members.
\end{definition}
\noindent This definition bestows the name ``$\emptyset$'' on a certain set. When we write down such a definition we must be sure of two things: that there exists such a set and that there cannot be more 
than one set having no members. The empty set axiom provides the first fact and extensionality provides the second.
Without both facts the symbol ``$\emptyset$'' would not be well defined.
\begin{definition}\hspace{1mm}
\begin{itemize}
\item For any sets $u$ and $v$, the \textbf{pair set} $\{u,v\}$ is the set whose members are $u$ and $v$.
\item For any sets $a$ and $b$, the \textbf{union} $a\cup b$ is the set whose members are those sets belonging either to $a$ or to $b$ (or both).
\item For any set $a$, the \textbf{power set} $\mathscr Pa$ is the set whose members are exactly the subsets of $a$.
\end{itemize}
\end{definition}
\noindent The existence and uniqueness proofs guaranteeing all of these definitions can be proved using the empty set axiom, the pairing axiom, the union axiom, and the power set axiom respectively,
each in combination with the extensionality axiom.\\
\vspace{1mm}\\
We can use the pairing and union together to form other finite sets. Given any $x$ we can denote the pair set $\{x,x\}$ as the \textit{singleton} $\{x\}$ (since the pair exists and is unique). 
For any given $x_1,x_2,x_3$ we can define
\begin{equation*}
\{x_1,x_2,x_3\}=\{x_1,x_2\}\cup\{x_3\}
\end{equation*}
(since the union exists and is unique for any two particular sets). Similarly we can define $\{x_1,x_2,x_3,x_4\}$ and so forth.\\
(next page)\newpage
\noindent\textbf{Notation}\\
Our existence axioms have been of the form ``there exists a set $B$ whose members are those sets $x$ satisfying the condition \_\_''
\begin{equation*}
\exists B\forall x(x\in B\leftrightarrow \_\_)
\end{equation*}
Where if some other sets $t_1,\ldots,t_k$ are involved in the condition, then the full version becomes
\begin{equation*}
\forall t_1\cdots\forall t_k\exists B\forall x(x\in B\leftrightarrow\_\_)
\end{equation*}
With the blank filled in be some expression involving $t_1,\ldots,t_k$ and $x$. The empty set axiom can be written as
\begin{equation*}
\exists B\forall x(x\in B\leftrightarrow x\neq x)
\end{equation*}
Now let us be more general and consider any statement of the form
\begin{equation*}
\forall t_1\cdots\forall t_k\exists B\forall x(x\in B\leftrightarrow\_\_)
\end{equation*}
If the statement were true, then the set $B$, by the statement itself, as well as by equivalence, can be named by use of the abstraction notation:
\begin{equation*}
B=\{x\mid\_\_\}
\end{equation*}
*My interpretation was that showing the existence and uniqueness of $B$ amounts to showing:
\begin{equation*}
\forall t_1\cdots\forall t_k[\exists B(\forall x(x\in B\leftrightarrow\_\_)\land 
\forall B'(\forall x(x\in B'\leftrightarrow\_\_)\to B'=B))]
\end{equation*}
The sets defined earlier can similarly be named in this notation:
\begin{align*}
\emptyset&=\{x\mid x\neq x\}\\
\{u,v\}&=\{x\mid x=u\text{ or }x=v\}\\
a\cup b&=\{x\mid x\in a\text{ or }x\in b\}\\
\mathscr Pa&=\{x\mid x\subseteq a\}
\end{align*}
Note that it is not the case that all statements of the general form are true. For instance 
\begin{equation*}
\exists B\forall x(x\in B\leftrightarrow x=x)
\end{equation*}
is false as it asserts the existence of a set $B$ to which every set belongs.\newpage

\subsection{Subset axioms}
\textit{Subset axioms}\\
For each formula \_\_ not containing $B$, the following is an axiom:
\begin{equation*}
\forall t_1\cdots\forall t_k\forall c\exists B\forall x(x\in B\leftrightarrow x\in c\land\_\_)
\end{equation*}
Given an existing set $c$, this axiom asserts the existence of a set whose members are exactly those sets in $c$ such that \_\_.\\
\vspace{1mm}\\
See that such a set must be the subset of an existing set $c$ (thus the name). The set can be named by use of a variation on the abstraction notation:
\begin{equation*}
B=\{x\in c\mid\_\_\}
\end{equation*}
\textbf{Intersection}\\
One of the subset axioms is
\begin{equation*}
\forall a\forall c\exists B\forall x(x\in B\leftrightarrow x\in c\land x\in a)
\end{equation*}
The axiom asserts the existence of the set we define to be the \textit{intersection} $c\cap a$ of $c$ and $a$.\\
\vspace{1mm}\\
\textbf{Relative complement}\\
We also have as a subset axiom 
\begin{equation*}
\forall A\forall B\exists S\forall x(x\in S\leftrightarrow x\in A\land x\notin B)
\end{equation*}
This set $S$ is the \textit{relative complement} of $B$ in $A$, denoted $A-B$.
\newpage

\subsection{Russell's Paradox}
\begin{theorem}
There is no set to which every set belongs.
\end{theorem}
\begin{proof}
Suppose, for contradiction, that there exists a set $A$ to which every set belongs. 
By the subset axiom we can assert 
\begin{equation*}
\forall A\exists B\forall x(x\in B\leftrightarrow x\in A\land x\notin x)
\end{equation*}
That is, the existence of 
\begin{equation*}
B=\{x\in A\mid x\notin x\}
\end{equation*}
By construction of $B$ we have
\begin{equation*}
\forall x(x\in B\leftrightarrow x\in A\land x\notin x)
\end{equation*}
and
\begin{equation*}
B\in B\leftrightarrow B\in A\land B\notin B
\end{equation*}
We know that $B\in A$. This can be used to show
\begin{equation*}
B\in B\leftrightarrow B\notin B\qedhere
\end{equation*}
\end{proof}
\noindent 
The idea here is that if $B$ were not a member of itself, then by definition $B$ should be in $B$. But if $B$ were a member of itself, then by definition it should not be a member of itself.
\newpage

\subsection{Improved Union Axiom}
The previously described union operation allowed us to consider the union of two sets, and by repeating the operation, the union of three sets and so on.
Suppose however we want the union of infinitely many sets:
\begin{equation*}
A=\{b_0,b_1,b_2,\ldots\}
\end{equation*}
For this we need a more general union operation:
\begin{align*}
\bigcup A&=\bigcup_ib_i\\
&=\{x\mid x\text{ belongs to some member $b_i$ of $A$}\}
\end{align*}
This leads us to define the union of any set $A$ as
\begin{align*}
\bigcup A&=\{x\mid x\text{ belongs to some member of $A$}\}\\
&=\{x\mid(\exists b\in A)x\in b\}
\end{align*}
We need an improved union axiom to include cases where $A$ were infinite, overcoming the limitation of defining unions strictly ``one by one''.\\
\vspace{1mm}\\
\textit{Union axiom}\\
For any set $A$, there exists a set $B$ whose elements are exactly the members of the members of $A$:
\begin{equation*}
\forall A\exists B\forall x[x\in B\leftrightarrow(\exists b\in A) x\in b]
\end{equation*}
For any $A$ we can define $\bigcup A$ as
\begin{equation*}
\bigcup A=\{x\mid(\exists b\in A)x\in b\}
\end{equation*}
See that for any two sets $a$ and $b$ we have
\begin{align*}
\bigcup\{a,b\}&=\{x\mid(\exists c\in\{a,b\})x\in c\}\\
&=\{x\mid x\in a\lor x\in b\}\\
&=a\cup b
\end{align*}
(one can check that the $\{x\mid x\in a\lor x\in b\}$ is the equivalent notation for the binary union.) This shows that our preliminary form of the union axiom can be discarded in favor of the new
form---the set $a\cup b$ produced by the preliminary form can also be obtained from the pairing and revised form of the union axiom.
\newpage

\subsection{Redundance of the preliminary union axiom}
\begin{theorem}
Given the pairing axiom
\begin{equation*}
\forall u\forall v\exists B\forall x(x\in B\leftrightarrow x=u\text{ or }x=v)
\end{equation*}
and the union axiom
\begin{equation*}
\forall A\exists B\forall x[x\in B\leftrightarrow(\exists b\in A) x\in b]
\end{equation*}
we can show
\begin{equation*}
\forall a\forall b\exists B\forall x(x\in B\leftrightarrow x\in a\text{ or }x\in b)
\end{equation*}
which is the preliminary union axiom determined earlier.
\end{theorem}
\begin{proof}
Let $a$ and $b$ be arbitrary sets. The pairing axiom asserts the existence of a set $A$ where
\begin{equation*}
\forall x(x\in A\leftrightarrow x=a\text{ or }x=b)
\end{equation*}
Now that we know set $A$ exists, the union axiom axiom asserts the existence of a set $B$ where
\begin{equation*}
\forall x[x\in B\leftrightarrow(\exists b\in A) x\in b]
\end{equation*}
Let $x$ be arbitrary.\\
\indent($\rightarrow$) First suppose $x\in B$. We can then declare some $y\in A$ such that $x\in y$. Since $y\in A$ we have $y=a\lor y=b$, and therefore $x\in a\lor x\in b$.\\
\indent($\leftarrow$) Now suppose that $x\in a\lor x\in b$. In the case where $x\in a$, we know that $x\in a\in A$, so $x\in B$. The case where $x\in b$ is similarly proven.
\end{proof}
\newpage

\subsection{Intersection}
\begin{theorem}
For any nonempty set $A$, there exists a unique set $B$ such that for any $x$, 
\begin{equation*}
x\in B\leftrightarrow x\text{ belongs to every member of $A$}
\end{equation*}
\end{theorem}
\begin{proof}
We first prove existence. We want to show
\begin{equation*}
\exists B(\forall x(x\in B\leftrightarrow\forall a\in A(x\in a)))
\end{equation*}
Since $A$ is nonempty we can let $c$ be some member of $A$. By the subset axiom we can assert 
\begin{equation*}
\exists B(x\in B\leftrightarrow x\in c\land \forall a\in A\backslash\{c\}(x\in a))
\end{equation*}
So we can declare some $B$ such that the above is true. Let $x$ be arbitrary.\\ 
\indent($\rightarrow$) First suppose that $x\in B$, then let $a\in A$. 
We have two cases; first suppose $a=c$, then we know $x\in c=a$. Now suppose that $x\neq c$; then since $x\in A$ we have $x\in A\backslash\{c\}$ and therefore $x\in a$.\\
\indent($\leftarrow$) Now suppose that $\forall a\in A(x\in a)$. Since $c\in A$, we must have $x\in c$. Let $a$ be some element of $A\backslash\{c\}$; clearly $a\in A$, so $x\in a$. We have 
now shown $x\in c\land \forall a\in A\backslash\{c\}(x\in a)$, so $x\in B$. Existence is proven.\\
\indent Uniqueness, as always, follows from extensionality. We consider some arbitrary $B'$ and assume that $\forall x(x\in B'\leftrightarrow\forall a\in A(x\in a))$, then show that $B'=B$ using
extensionality.
\end{proof}
\noindent In contrast to the union operation, no special axiom is needed to justify the intersection operation. This theorem permits defining a unique intersection set for every nonempty set.
We proved that for any nonempty $A$,
\begin{equation*}
\exists B(\forall x(x\in B\leftrightarrow\forall a\in A(x\in a)))
\end{equation*}
and that this set was unique for each $A$. Using the earlier notation we name this set
\begin{equation*}
\bigcap A=\{x\mid x\text{ belongs to every member of $A$}\}
\end{equation*}
An edge case should be considered: our theorem proves existence of the intersection $\bigcap A$ for all nonempty $A$; what happens in the case where $A=\emptyset$? In other words,
is it the case that
\begin{equation*}
\exists B(\forall x(x\in B\leftrightarrow \forall a\in\emptyset(x\in a)))
\end{equation*}
We can show that this implies (by vacuous truth)
\begin{equation*}
\exists B(\forall x(x\in B))
\end{equation*}
which would contradict russells paradox. 
\newpage

\section{Set algebra}
The union operation for any two sets exists by the pairing, union, and extensionality axioms.
\begin{equation*}
A\cup B=\{x\mid x\in A\lor x\in B\}
\end{equation*}
The intersection operation for any two sets exists by the subset and extensionality axioms.
\begin{equation*}
A\cap B=\{x\mid x\in A\land x\in B\}
\end{equation*}
Also by the subset and extensionality axioms, we have the \textit{relative complement $A-B$ of $B$ in $A$}.
\begin{equation*}
A-B=\{x\in A\mid x\notin B\}
\end{equation*}
also sometimes denoted as $A\backslash B$.\\
\vspace{1mm}\\
Note that we cannot form (as a set) the ``absolute complement'' of $B$, $\{x\mid x\neq B\}$. In this case the union with $B$, which must exist axiomatically, would be a set of all sets, which 
would contradict russell's paradox.\\
\vspace{1mm}\\
The study of the operations of union $(\cup)$, intersection $(\cap)$, and relative complementation $(-)$, together with the inclusion relation $(\subseteq)$, is called the \textit{algebra of sets}.
The following identities, which hold for any sets, are some elementary facts of the algebra of sets:\\
\vspace{1mm}\\
\textit{Commutative laws}
\begin{equation*}
A\cup B=B\cup A\quad\text{and}\quad A\cap B=B\cap A
\end{equation*}
\textit{Associative laws}
\begin{align*}
A\cup(B\cup C)&=(A\cup B)\cup C\\
A\cap(B\cap C)&=(A\cap B)\cap C
\end{align*}
Proofs of these follow directly from the commutativity and associativity of the logical OR and AND.\\
(next page)\newpage
\noindent\textit{Distributive laws}
\begin{align*}
A\cap(B\cup C)&=(A\cap B)\cup(A\cap C)\\
A\cup(B\cap C)&=(A\cup B)\cap(A\cup C)
\end{align*}
\begin{proof}
First we show $A\cap(B\cup C)=(A\cap B)\cup(A\cap C)$. Let $x$ be arbitrary.\\
\indent($\rightarrow$) Suppose $x\in A\cap(B\cup C)$. Then $x\in A$ and $x\in B\cup C$. In the case where $x\in B$, then $x\in A\cap B$. In the case where $x\in C$, 
then $x\in A\cap C$. So we have $x\in A\cap B\lor x\in A\cap C$ and $x\in(A\cap B)\cup(A\cap C)$.\\
\indent($\leftarrow$) Suppose $x\in (A\cap B)\cup(A\cap C)$. Then $x\in (A\cap B)\lor x\in(A\cap C)$. In the case where $x\in (A\cap B)$ then $x\in A$ and $x\in B$. So $x\in B\cup C$ and 
$x\in A\cap(B\cup C)$. In the case where $x\in(A\cap C)$ then $x\in A$ and $x\in C$. Again $x\in B\cup C$ and $x\in A\cap(B\cup C)$. We are done.\\
\indent Now we show $A\cup(B\cap C)=(A\cup B)\cap(A\cup C)$. Let $x$ be arbitrary.\\
\indent($\rightarrow$) Suppose $x\in A\cup(B\cap C)$. Then $x\in A$ or $x\in B\cap C$. In the case where $x\in A$ we have both $x\in A\cup B$ and $x\in A\cup C$, so $x\in(A\cup B)\cap(A\cup C)$. 
In the case where $x\in B\cap C$, then $x\in B$ and $x\in C$. So $x\in(A\cup B)$ and $x\in(A\cup C)$ and $x\in(A\cup B)\cap(A\cup C)$.\\
\indent($\leftarrow$) Suppose $x\in(A\cup B)\cap(A\cup C)$. We have $x\in(A\cup B)$ and $x\in(A\cup C)$. We have two cases. Suppose first that $x\in A$; then $x\in A\cup(B\cap C)$. 
Now suppose $x\notin A$. Then since $x\in(A\cup B)$ and $x\in(A\cup C)$ we must have $x\in B$ and $x\in C$. So $x\in B\cap C$ and $x\in A\cup(B\cap C)$.
\end{proof}
\noindent\textit{De Morgan's laws}
\begin{align*}
C-(A\cup B)&=(C-A)\cap(C-B)\\
C-(A\cap B)&=(C-A)\cup(C-B)
\end{align*}
\begin{proof}
First we show $C-(A\cup B)=(C-A)\cap(C-B)$. Let $x$ be arbitrary.\\
\indent($\rightarrow$) Suppose $x\in C-(A\cup B)$. Then $x\in C$ and $x\notin A\cup B$, meaning $\neg(x\in A\cup B)$, $\neg(x\in A\lor x\in B)$, and $x\notin A\land x\notin B$. 
So since $x\in C$, we have $x\in C-A$ and $x\in C-B$, and therefore $x\in(C-A)\cap(C-B)$.\\
\indent($\leftarrow$) Suppose $x\in(C-A)\cap(C-B)$. Then $x\in C$, $x\notin A$, and $x\notin B$.
We therefore have $\neg(x\in A\lor x\in B)$ and $x\notin A\cup B$. So $x\in C-(A\cup B)$. We are done.\\
\indent Now we show $C-(A\cap B)=(C-A)\cup(C-B)$. Let $x$ be arbitrary.\\
\indent ($\rightarrow$) Suppose $x\in C-(A\cap B)$. Then $x\in C$ and $\neg(x\in A\land x\in B)$. So $x\notin A$ or $x\notin B$. In the case where $x\notin A$, $x\in C-A$.
In the case where $x\notin B$, $x\in C-B$. We therefore have $x\in C-A$ or $x\in C-B$, and $x\in(C-A)\cup(C-B)$.\\
\indent ($\leftarrow$) Suppose $x\in(C-A)\cup(C-B)$. We have two cases. First suppose $x\in C-A$, then $x\in C$ and $x\notin A$. The latter implies $\neg(x\in A\land x\in B)$ and $x\notin A\cap B$,
so $x\in C-(A\cap B)$. Now suppose $x\in C-B$. In a similar manner this implies $x\in C$ and $x\notin A\cap B$, and therefore $x\in C-(A\cap B)$.
\end{proof}
\noindent(next page)\newpage
\noindent One generally considers sets as subsets of some larger set or ``space'' $S$. Assume then that $A$ and $B$ are subsets of $S$. We can then abbreviate $S-A$ as simply $-A$, the set $S$
being understood as fixed. In this abbreviation De Morgan's laws become
\begin{align*}
-(A\cup B)&=-A\cap-B\\
-(A\cap B)&=-A\cup-B
\end{align*}
\noindent\textit{Identities involving $\emptyset$}
\begin{align*}
A\cup\emptyset&=A\\
A\cap\emptyset&=\emptyset\\
A\cap(C-&A)=\emptyset
\end{align*}
\begin{proof}
We show $A\cup\emptyset=A$. Let $x$ be arbitrary. First suppose that $x\in A\cup\emptyset$. This implies that $x\notin\emptyset\to x\in A$. Therefore $x\in A$. The other direction is clearly true.\\
\indent Both of the other two statements can be proved by extensionality, where both directions in each statement are vacuously true.
\end{proof}
\noindent\textit{Inclusion}\\
Under the assumption that $A\subseteq S$ (and that $S-A$ can be abbreviated as $-A$), we have
\begin{align*}
A\cup S&=S\\
A\cap S&=A\\
A\cup-&A=S\\
A\cap-&A=\emptyset
\end{align*}
\begin{proof}
First we show $A\cup S=S$. Let $x$ be arbitrary. Suppose that $x\in A\cup S$; then $x\in A$ or $x\in S$. In the case where $x\in A$, since $A\subseteq S$ then $x\in S$. The case where $x\in S$ is 
self-evident. Now suppose that $x\in S$, then clearly $x\in A\cup S$. We are done.\\
\indent Next we show $A\cap S=A$. Let $x$ be arbitrary. Suppose $x\in A\cap S$. This clearly implies $x\in A$. Now suppose that $x\in A$. Since $A\subseteq S$ we also have $x\in S$ and therefore 
$x\in A\cap S$.\\
\indent To show $A\cup-A=S$, let $x$ be arbitrary and suppose $x\in A\cup -A$. This means
$x\in A\lor(x\in S\land x\notin A)$. In the case where $x\in A$ we know that $A\subseteq S$ so $x\in S$. The other case where $x\in S\land x\notin A$ is self-evident. Now suppose $x\in S$; we have 
two cases. In the first case suppose $x\in A$. Then clearly $x\in A\cup-A$. In the other case $x\notin A$. Then $x\in S-A$ and $x\in A\cup-A$.\\
\indent The last statement follows from a previously proven identity. Namely that for any two sets $A$ and $C$ we have $A\cap(C-A)=\emptyset$.
\end{proof}
\noindent(next page)\newpage
\noindent\textit{Inclusion: Monotonicity properties}
\begin{align*}
A\subseteq B&\to A\cup C\subseteq B\cup C\\
A\subseteq B&\to A\cap C\subseteq B\cap C\\
A\subseteq B&\to\bigcup A\subseteq\bigcup B
\end{align*}
\begin{proof}
For the first property, suppose $A\subseteq B$. Let $x$ be an arbitrary element of $A\cup C$. Then $x\in A$ or $x\in C$. In the case where $x\in A$, since $A\subseteq B$ we also have $x\in B$ and 
$x\in B\cup C$. 
In the case where $x\in C$ we have $x\in B\cup C$.\\
\indent For the second property, again suppose $A\subseteq B$. Let $x$ be an arbitrary element of $A\cap C$. Then $x\in A$ and $x\in C$. Since $A\subseteq B$, $x\in B$; so $x\in B\cap C$.\\
\indent For the last property, suppose $A\subseteq B$ and let $x$ be an arbitrary element of $\bigcup A$. Then there is some $a\in A$ such that $x\in a$. Since $A\subseteq B$, $x\in a\in B$; so
$x\in\bigcup B$.
\end{proof}
\noindent\textit{Antimonotone properties}
\begin{align*}
A\subseteq B&\to C-B\subseteq C-A\\
\emptyset\neq A\subseteq B&\to\bigcap B\subseteq\bigcap A
\end{align*}
\begin{proof}
For the first property, suppose $A\subseteq B$ and let $x$ be an arbitrary element of $C-B$. This means $x\in C$ and $x\notin B$. The contrapositive of the fact that $A\subseteq B$ 
shows that $x\notin A$. So $x\in C-A$.\\
\indent For the second property, suppose $A$ is nonempty and $A\subseteq B$ (which also means that $B$ is nonempty). Let $x$ be an arbitrary element of $\bigcap B$. Let $a$ be some element of $A$. 
Since $A\subseteq B$, $a\in B$. Since $x\in\bigcap B$ we then have $x\in a$.
\end{proof}
\noindent(next page)\newpage
\noindent\textit{Distributive laws}
\begin{align*}
A\cup\bigcap B&=\bigcap\{A\cup X\mid X\in B\}\quad\text{for $B\neq\emptyset$}\\
A\cap\bigcup B&=\bigcup\{A\cap X\mid X\in B\}
\end{align*}
The set $\{A\cup X\mid X\in B\}$ is an extension of the abstraction notation; read ``the set of all $A\cup X$ such that $X\in B$''. It defines the unique set $D$ such that
\begin{equation*}
\forall x(x\in D\leftrightarrow\exists X\in B(x=A\cup X))
\end{equation*}
The existence of such a set $D$ can be proved by observing that $A\cup X\subseteq A\cup\bigcup B$, which means that $D$ is a subset of $\mathscr P(A\cup\bigcup B)$. A similar approach 
can be used to assert the existence of $\{A\cap X\mid X\in B\}$.
\begin{proof} 
(First statement) First we prove the existence of $\{A\cup X\mid X\in B\}$. We do this by showing that for arbitrary $x$, $A$, and $B$,
\begin{equation*}
\exists X\in B(x=A\cup X)\to x\in\mathscr P(A\cup\bigcup B)
\end{equation*}
Suppose there exists some $X\in B$ such that $x=A\cup X$. Let $y$ be some arbitrary element of $x$.
Then $y\in A\cup X$. In the case where $y\in A$ we clearly have $y\in A\cup\bigcup B$. In the case where $y\in X$, since $X\in B$ we then have $y\in\bigcup B$ and $y\in A\cup\bigcup B$.
This shows that $x\subseteq A\cup\bigcup B$ and $x\in\mathscr P(A\cup\bigcup B)$.
As such we have
\begin{equation*}
\forall A\forall B\forall x[\exists X\in B(x=A\cup X)\leftrightarrow x\in\mathscr P(A\cup\bigcup B)\land\exists X\in B(x=A\cup X)]
\end{equation*}
The statement
\begin{equation*}
\forall A\forall B\exists C(\forall x(x\in C\leftrightarrow x\in\mathscr P(A\cup\bigcup B)\land\exists X\in B(x=A\cup X)))
\end{equation*}
Is true by the subset axiom. These two statements can be used to show
\begin{equation*}
\forall A\forall B\exists C(\forall x(x\in C\leftrightarrow\exists X\in B(x=A\cup X)))
\end{equation*}
Proving the existence of $\{A\cup X\mid X\in B\}$ for arbitrary $A$ and $B$, where uniqueness follows from extensionality.\\
(next page)\newpage
Now we prove the first property.
\begin{equation*}
A\cup\bigcap B=\bigcap\{A\cup X\mid X\in B\}\quad\text{for $B\neq\emptyset$}
\end{equation*}
Let $x$ be arbitrary.\\
\indent($\rightarrow$) Suppose $x\in A\cup\bigcap B$. This means that either $x\in A$ or $x\in\bigcap B$.
Let $a$ be some arbitrary element of $\{A\cup X\mid X\in B\}$; this means that there exists some $X\in B$ such that $a=A\cup X$. In the case where $x\in A$, we clearly have $x\in A\cup X=a$.
In the case where $x\in\bigcap B$, since $X\in B$ we must have $x\in X$. Therefore $x\in A\cup X=a$.\\
\indent($\leftarrow$) Now suppose that $x\in\bigcap\{A\cup X\mid X\in B\}$. This means $\forall a\in\{A\cup X\mid X\in B\}(x\in a)$. We have 2 cases. First suppose $x\in A$; then 
$x\in A\cup\bigcap B$. Now suppose $x\notin A$; we will show that $x\in\bigcap B$. Let $b\in B$; then we know $A\cup b\in\{A\cup X\mid X\in B\}$. So $x\in A\cup b$. Since $x\notin A$ this must 
mean that $x\in b$. So $x\in\bigcap B$ and $x\in A\cup\bigcap B$.
\end{proof}
\begin{proof}(Second statement) First we prove the existence of $\{A\cap X\mid x\in B\}$, defined as the unique set $C$ where for arbitrary $A$ and $B$,
\begin{equation*}
\forall x(x\in C\leftrightarrow\exists X\in B(x=A\cap X))
\end{equation*}
We first show
\begin{equation*}
\forall A\forall B\forall x(\exists X\in B(x=A\cap X)\to x\in\mathscr P(A\cap\bigcup B))
\end{equation*}
Let $A$, $B$, and $x$ be arbitrary. Suppose there exists $X\in B$ such that $x=A\cap X$.
Let $y$ be some arbitrary element of $x$. Then $y\in A$ and $y\in X\in B$, meaning $y\in\bigcup B$.
So $y\in A\cup\bigcup B$ and $x\in\mathscr P(A\cup\bigcup B)$.\\
\indent We now know
\begin{equation*}
\forall A\forall B\forall x(\exists X\in B(x=A\cap X)\leftrightarrow x\in\mathscr P(A\cap\bigcup B)\land\exists X\in B(x=A\cap X))
\end{equation*}
By the subset axiom we can assert
\begin{equation*}
\forall A\forall B\exists C(\forall x(x\in C\leftrightarrow x\in\mathscr P(A\cap\bigcup B)\land\exists X\in B(x=A\cap X)))
\end{equation*}
Using these two facts we can prove
\begin{equation*}
\forall A\forall B\exists C(\forall x(x\in C\leftrightarrow x\in\exists X\in B(x=A\cap X)))
\end{equation*}
Proving the existence of $\{A\cap X\mid X\in B\}$ for arbitrary $A$ and $B$, where uniqueness follows from extensionality.\\
(next page)\newpage
Now we prove the second property.
\begin{equation*}
A\cap\bigcup B=\bigcup\{A\cap X\mid X\in B\}
\end{equation*}
Let $x$ be arbitrary.\\
\indent($\rightarrow$) Suppose $x\in A\cap\bigcup B$. Then $x\in A$ and $x\in\bigcup B$, meaning we can declare some $b\in B$ such that $x\in b$. We know $x\in A\cap b$. 
Since $A\cap b\in\{A\cap X\mid X\in B\}$, we then have $x\in\bigcup\{A\cap X\mid X\in B\}$.\\
\indent($\leftarrow$) Suppose now that $x\in\bigcup\{A\cap X\mid X\in B\}$ then we can declare some $a\in\{A\cap X\mid X\in B\}$ such that $x\in a$. This means that 
we can declare some $X\in B$ such that $a=A\cap X$. So $x\in A$ and $x\in X\in B$, which means
$x\in\bigcup B$. So $x\in A\cap\bigcup B$.
\end{proof}
\noindent\textit{De Morgan's laws (for $A\neq\emptyset$)}
\begin{align*}
C-\bigcup A&=\bigcap\{C-X\mid X\in A\}\\
C-\bigcap A&=\bigcup\{C-X\mid X\in A\}
\end{align*}
Existence of $\{C-X\mid X\in A\}$ can be proven by noticing that $X\in A$ implies $\bigcap A\subseteq X$, which implies $C-X\subseteq C-\bigcap A$.
\begin{proof}
We first prove existence of $\{C-X\mid X\in A\}$. That is, we prove
\begin{equation*}
\forall A\forall C(\exists D\forall x(x\in D\leftrightarrow\exists X\in A(x=C-X)))
\end{equation*}
We start by showing that for nonempty $A$,
\begin{equation*}
\forall A\forall C\forall x(\exists X\in A(x=C-X)\to x\in\mathscr P(C-\bigcap A))
\end{equation*}
Letting $A, C,$ and $x$ be arbitrary, suppose there exists some $X\in A$ such that $x=C-X$. Let $y$ be some arbitrary element of $x$. 
Then $y\in C$ and $y\notin X$. For contradiction suppose $y\in\bigcap A$; since $X\in A$ this would mean $y\in X$, which is a contradiction. So $y\in C-\bigcap A$, $x\subseteq C-\bigcap A$, and
$x\in\mathscr P(C-\bigcap A)$. We are done.\\
\indent By the subset axiom we can assert
\begin{equation*}
\forall A\forall C\exists D\forall x(x\in D\leftrightarrow x\in\mathscr P(C-\bigcap A)\land\exists X\in A(x=C-X))
\end{equation*}
Using these two facts we can prove
\begin{equation*}
\forall A\forall C(\exists D\forall x(x\in D\leftrightarrow\exists X\in A(x=C-X)))
\end{equation*}
Which proves the existence of $\{C-X\mid X\in A\}$ for arbitrary $A$ and $C$. Uniqness follows from extensionality.\\
(next page)\newpage
Now we prove the first property---that for nonempty $A$,
\begin{equation*}
C-\bigcup A=\bigcap\{C-X\mid X\in A\}
\end{equation*}
Let $x$ be arbitrary.\\
\indent($\rightarrow$) Suppose $x\in C-\bigcup A$. Then $x\in C$ and $x\notin\bigcup A$. 
Suppose arbitrary $a\in\{C-X\mid X\in A\}$. Then there exists some $X\in A$ such that 
$a=C-X$. Suppose for contradiction that $x\in X$; since $X\in A$ this would mean $x\in\bigcup A$, which is a contradiction. Therefore $x\in C-X=a$. Since $a$ was arbitrary we therefore have 
$x\in\bigcap\{C-X\mid X\in A\}$.\\
\indent($\leftarrow$) Now suppose $x\in\bigcap\{C-X\mid X\in A\}$. Since $A$ is nonempty we can declare some $X\in A$. Then $C-X\in\{C-X\mid X\in A\}$, and $x\in C-X$. So we have $x\in C$.
Now suppose for contradiction that $x\in\bigcup A$. Then we can declare some $X_0\in A$ such that $x\in X_0$. $C-X_0\in\{C-X\mid X\in A\}$, so $x\in C-X_0$ and $x\notin X_0$, which is a 
contradiction. So we have $x\in C-\bigcup A$. This proves the first property.\\
\indent Now for the second property. For any nonempty $A$,
\begin{equation*}
C-\bigcap A=\bigcup\{C-X\mid X\in A\}
\end{equation*}
Let $x$ be arbitrary\\
\indent($\rightarrow$) Suppose $x\in C-\bigcap A$. Then $x\in C$ and $x\notin\bigcap A$. The latter implies $\exists a\in A(x\notin a)$. So there is some $a\in A$ such that $x\notin a$.
We know $x\in C-a\in\{C-X\mid X\in A\}$; so $x\in\bigcup\{C-X\mid X\in A\}$.\\
\indent($\leftarrow$) Suppose $x\in\bigcup\{C-X\mid X\in A\}$. Then there exists some $a\in\{C-X\mid X\in A\}$ such that $x\in a$. There then exists some $X\in A$ such that $a=C-X$.
So $x\in C$ and $x\notin X$. For contradiction, suppose $x\in\bigcap A$. Since $X\in A$ this would imply that $x\in X$, which is a contradiction. So $x\in C-\bigcap A$. We are done.
\end{proof}
\newpage

\chapter{Relations and Functions}
\section{Ordered Pairs}
The pair set $\{a,b\}$ can be thought of as an unordered pair, since $\{a,b\}=\{b,a\}$. We want to define a set $\langle x,y\rangle$ that uniquely encodes both what $x,y$ are, and what order 
they are in. That is, 
\begin{equation*}
\forall x\forall y\forall u\forall v(\langle x,y\rangle=\langle u,v\rangle\leftrightarrow(x=u\land y=v))
\end{equation*}
Any definition of $\langle x,y\rangle$ that satisfies the above will suffice. For an example of definitions that \textit{fail this requirement},
if we define $\langle x,y\rangle_1=\{x,y\}$, then for $x\neq y$, $\langle x,y\rangle_1=\{x,y\}=\{y,x\}=\langle y,x\rangle_1$ even though $x\neq y$.\\
\vspace{1mm}\\
The most conventional construction was given by Kazimierz Kuratowski in 1921:
\begin{definition}
$\langle x,y\rangle$ is defined to be $\{\{x\},\{x,y\}\}$.
\end{definition}
\noindent We must prove that this definition succeeds in capturing the desired property.
\begin{theorem}
For arbitrary $u,v,x,y$, $\langle u,v\rangle=\langle x,y\rangle$ iff $u=x$ and $v=y$.
\end{theorem}
\begin{proof}
The left direction is trivial. If $u=x$ and $v=y$, then $\{\{x\},\{x,y\}\}$ is identical to $\{\{u\},\{u,v\}\}$.\\
\indent For the right direction,
suppose $\langle u,v\rangle=\langle x,y\rangle$. We have two cases. First suppose $x=y$. 
Then $\langle x,y\rangle=\{\{x\},\{x,y\}\}=\{\{x\},\{x,x\}\}=\{\{x\},\{x\}\}=\{\{x\}\}$ and then
$\{\{x\}\}=\{\{u\},\{u,v\}\}$. This means that $\{x\}=\{u,v\}$ and $y=x=u=v$. So clearly $u=x$ and $v=y$. For the other case suppose $x\neq y$. We know 
$\{\{x\},\{x,y\}\}=\{\{u\},\{u,v\}\}$. See that $\{u\}=\{x\}\lor\{u\}=\{x,y\}$; the latter cannot be the case, so we must have $\{u\}=\{x\}$ and $u=x$. We know that $\{x,y\}\neq\{u\}$ 
since $x\neq y$, so we must have $\{x,y\}=\{u,v\}=\{x,v\}$. This leaves us with $y=x\lor y=v$, so we can conclude that $y=v$.
\end{proof}
\noindent This allows us to unambiguously define the \textit{first coordinate} of $\langle x,y\rangle$ to be $x$ and the \textit{second coordinate} to be $y$.
\newpage

\subsection{Cartesian product}
Suppose that we have two sets $A$ and $B$, and we form ordered pairs $\langle x,y\rangle$ with $x\in A$ and $y\in B$. The collection of all such pairs is called the \textit{Cartesian product}
$A\times B$ of $A$ and $B$:
\begin{equation*}
A\times B=\{\langle x,y\rangle\mid x\in A\land y\in B\}
\end{equation*}
We must verify that this collection is actually a set before the definition is legal.
\begin{lemma}
For arbitrary $x,y,C$, if $x\in C$ and $y\in C$, then $\langle x,y\rangle\in\mathscr P\mathscr PC$.
\end{lemma}
\begin{proof}
Suppose $x\in C$ and $y\in C$. Then $\{x\}\subseteq C$ and $\{x,y\}\subseteq C$. So $\{x\}\in\mathscr PC$ and $\{x,y\}\in\mathscr PC$. So $\{\{x\},\{x,y\}\}\subseteq\mathscr PC$ and 
$\{\{x\},\{x,y\}\}\in\mathscr{PP}C$.
\end{proof}
\noindent Now to show existence of $A\times B=\{\langle x,y\rangle\mid x\in A\land y\in B\}$.
\begin{proof}
We first show
\begin{equation*}
\forall A\forall B\forall t(\exists x\in A\exists y\in B(t=\langle x,y\rangle)\to t\in\mathscr{PP}(A\cup B))
\end{equation*}
Letting $A,B,$ and $t$ be arbitrary, suppose we can declare $x\in A$ and $y\in B$ such that $t=\langle x,y\rangle$. We have $x\in A\cup B$ and $y\in A\cup B$; by the previous lemma we then
have $t=\langle x,y\rangle\in\mathscr{PP}(A\cup B)$.\\
\indent By the subset axiom we can assert
\begin{equation*}
\forall A\forall B\exists D\forall t(t\in D\leftrightarrow t\in\mathscr{PP}(A\cup B)\land\exists x\in A\exists y\in B(t=\langle x,y\rangle))
\end{equation*}
Using these two facts we can show
\begin{equation*}
\forall A\forall B\exists D\forall t(t\in D\leftrightarrow\exists x\in A\exists y\in B(t=\langle x,y\rangle))
\end{equation*}
Proving the existence of $\{\langle x,y\rangle\mid x\in A\land y\in B\}$ for arbitrary $A$ and $B$. Uniqueness follows from extensionality.
\end{proof}
\newpage

\section{Relations}
\begin{definition}
A \textbf{relation} is a set of ordered pairs.
\end{definition}
\noindent Any set of ordered pairs is some relation, even if a peculiar one. For a relation $R$, we sometimes write $xRy$ in place of $\langle x,y\rangle\in R$.
\begin{definition}
We define the \textbf{domain} of $R$ (dom $R$), the \textbf{range} of $R$ (ran $R$), and the \textbf{field} of $R$ (fld $R$) by
\begin{align*}
x\in\text{dom}\,R&\leftrightarrow\exists y(\langle x,y\rangle\in R)\\
x\in\text{ran}\,R&\leftrightarrow\exists t(\langle t,x\rangle\in R)\\
\text{fld}\,R&=\text{dom}\,R\cup\text{ran}\,R
\end{align*}
\end{definition}
\noindent Again we must justify the existence of the domain and the range. 
\begin{lemma}
For arbitrary $A,x,y$, if $\langle x,y\rangle\in A$, then $x$ and $y$ belong to $\bigcup\bigcup A$.
\end{lemma}
\begin{proof}
We assume $\{\{x\},\{x,y\}\}\in A$. Consequently, $\{x,y\}\in\bigcup A$ since it belongs to a member of $A$. In a similar manner we can conclude that $x\in\bigcup\bigcup A$ and
$y\in\bigcup\bigcup A$.
\end{proof}
\noindent Now to prove existence. 
\begin{proof}
Starting with the domain, we want to show
\begin{equation*}
\forall R\exists D\forall x(x\in D\leftrightarrow\exists y(\langle x,y\rangle\in R))
\end{equation*}
We start by proving
\begin{equation*}
\forall R\forall x(\exists y(\langle x,y\rangle\in R)\to x\in\bigcup\bigcup R)
\end{equation*}
Letting $R$ and $x$ be arbitrary, and supposing that there exists $y$ such that $\langle x,y\rangle\in R$, by the previous lemma we have $x\in\bigcup\bigcup R$.\\
\indent The subset axioms allow us to assert
\begin{equation*}
\forall R\exists D\forall x(x\in D\leftrightarrow x\in\bigcup\bigcup R\land\exists y(\langle x,y\rangle\in R))
\end{equation*}
Existence follows from these two facts. Uniqueness follows from extensionality.\\
\indent Now for the range. We want to show
\begin{equation*}
\forall R\exists D\forall x(x\in D\leftrightarrow\exists t(\langle t,x\rangle\in R))
\end{equation*}
Again using the previous lemma we can easily prove
\begin{equation*}
\forall R\forall x(\exists t(\langle t,x\rangle\in R)\to x\in\bigcup\bigcup R)
\end{equation*}
and then using the subset axiom to assert
\begin{equation*}
\forall R\exists D\forall x(x\in D\leftrightarrow x\in\bigcup\bigcup R\land\exists t(\langle t,x\rangle\in R))
\end{equation*}
the desired result follows. Uniqueness follows from extensionality.
\end{proof}\newpage

\subsection{$n$-ary Relations}
We can extend the ideas behind ordered pairs to the case of ordered triples and, more generally, to ordered $n$-tuples. For triples we define
\begin{equation*}
\langle x,y,z\rangle=\langle\langle x,y\rangle,z\rangle
\end{equation*}
Similarly we can form ordered quadruples:
\begin{equation*}
\langle x_1,x_2,x_3,x_4\rangle=\langle\langle x_1,x_2,x_3\rangle,x_4\rangle=\langle\langle\langle x_1,x_2\rangle,x_3\rangle,x_4\rangle
\end{equation*}
We define an \textit{$n$-ary relation on $A$} to be a set of ordered $n$-tuples with all components in $A$. Thus a binary (2-ary) relation on $A$ is just a subset of $A\times A$. 
A ternary (3-ary) relation on $A$ is a subset of $(A\times A)\times A$.

\section{Functions}
\begin{definition}
A \textbf{function} is a relation $F$ such that for each $x$ in dom$\,F$ there is only one $y$ such that $xFy$.
\begin{equation*}
\forall x\in\text{dom$\,F$}\exists!y(xFy)
\end{equation*}
For a function $F$ and a $x$ in dom$\,F$, the unique $y$ such that $xFy$ is called the \textbf{value of $F$ at $x$} and is denoted $F(x)$. Thus $\langle x,F(x)\rangle\in F$.
\end{definition}
\noindent To avoid confusion, this ``$F(x)$'' notation should only be used when $F$ is a function and $x\in\text{dom}\,F$.
\begin{definition}
For sets $A$ and $B$, we say that $F$ is a function \textit{from $A$ to $B$} or that $F$ \textit{maps $A$ into $B$}
\begin{equation*}
F:A\to B
\end{equation*}
iff $F$ is a function, dom$\,F=A$, and ran$\,F\subseteq B$. 
\end{definition}
\noindent Note the unequal treatment of $A$ and $B$ here---we demand only that ran$\,F\subseteq B$.
\begin{definition}
$F$ is a function from $A$ \textbf{onto} $B$ if $F$ is a function from $A$ to $B$, and ran$\,F=B$.
\end{definition}
\noindent Thus any function $F$ maps its domain onto its range. The word ``onto'' depends both on $F$ and on the set $B$. 
\begin{definition}
A function $F$ is \textbf{one-to-one} iff for each $y\in\text{ran}\,F$ there is only one $x$ such that $xFy$.
\begin{equation*}
\forall y\in\text{ran}\,F\exists!x(xFy)
\end{equation*}
One-to-one functions are sometimes called \textbf{injections}.
\end{definition}
\noindent(next page)
\newpage
\noindent I use this page to prove a few equivalences of alternative definitions.
\begin{theorem}
For a function $F$,
\begin{equation*}
\forall y\in\text{ran}\,F\exists!x(xFy)\leftrightarrow
\forall x_1\in\text{dom}\,F\forall x_2\in\text{dom}\,F(F(x_1)=F(x_2)\to x_1=x_2)
\end{equation*}
\end{theorem}
\begin{proof} ($\rightarrow$)
Suppose $\forall y\in\text{ran}\,F\exists!x(xFy)$. This can be rewritten as
\begin{equation*}
\forall y\in\text{ran}\,F(\exists x(xFy)\land\forall x_1\forall x_2(x_1Fy\land x_2Fy\to x_1=x_2))
\end{equation*}
Suppose $x_1$ and $x_2$ are elements of dom$\,F$ such that $F(x_1)=F(x_2)$ (we know that $F(x_1)$ and $F(x_2)$ exist and are unique since $F$ is a function and $x_1$ and $x_2$ are in
the domain of $F$.) We know $\langle x_1,F(x_1)\rangle\in F$ and $\langle x_2,F(x_2)\rangle\in F$ so both $F(x_1)$ and $F(x_2)$ are in the range of $F$. We will denote $F(x_1)=F(x_2)=y$. 
We then have $x_1Fy$ and $x_2Fy$ for $y\in\text{ran}\,F$. Using our initial assumption we can conclude that $x_1=x_2$.\\
\indent($\leftarrow$) Suppose now that the right side is true. We want to show
\begin{equation*}
\forall y\in\text{ran}\,F(\exists x(xFy)\land\forall x_1\forall x_2(x_1Fy\land x_2Fy\to x_1=x_2))
\end{equation*}
Let $y$ be an arbitrary element of ran$\,F$. $\exists x(xFy)$ follows by definition. Let $x_1$ and $x_2$ be arbitrary such that $x_1Fy$ and $x_2Fy$. Then $x_1$ and $x_2$ are in the domain of $F$.
Since $F$ is a function, $y=F(x_1)=F(x_2)$ it follows from our initial assumption that $x_1=x_2$.
\end{proof}
\begin{theorem}
Supposing $F$ is a function from $A$ to $B$,
\begin{equation*}
\text{ran}\,F=B\leftrightarrow\forall y\in B\exists x\in A(xFy)
\end{equation*}
\end{theorem}
\begin{proof}
\indent ($\rightarrow$) Suppose $\text{ran}\,F=B$. Let $y$ be an arbitrary element of $B$.
Then by our assumption, $y\in\text{ran}\,F$. By definition, there exists some $x$ such that $xFy$.
$x$ is in the domain of $F$, so since $F:A\to B$, $x\in A$.\\
\indent ($\leftarrow$) Suppose now that $\forall y\in B\exists x\in A(xFy)$. Let $y$ be arbitrary. First suppose $y\in\text{ran}\,F$. Then since $F:A\to B$, $\text{ran}\,F\subseteq B$ and $y\in B$.
Now suppose $y\in B$. Then by the initial assumption there exists some $x\in A$ such that $xFy$.
This implies that $y\in\text{ran}\,F$.
\end{proof}
\newpage

\subsection{More definitions}
It will occasionally be useful to apply the concept of ``one-to-one'' to relations that are not functions. The phrase seems inapproprate in the context of nonfunctions, so in such a context we use
the phrase ``single-rooted''.
\begin{definition}
A set $R$ is \textit{single-rooted} iff for each $y\in\text{ran}\,R$ there is only one $x$ such that $xRy$.
\begin{equation*}
\forall y\in\text{ran}\,F\exists!x(xRy)
\end{equation*}
For a function, it is single-rooted iff it is one-to-one.
\end{definition}
\noindent The following can be defined for arbitrary sets $A,F,$ and $G$:
\begin{definition}\hspace{1mm}\\
The \textbf{inverse} of $F$ is the set
\begin{equation*}
F^{-1}=\{\langle u,v\rangle\mid vFu\}
\end{equation*}
The \textbf{composition} of $F$ and $G$ is the set
\begin{equation*}
F\circ G=\{\langle u,v\rangle\mid\exists t(uGt\land tFu)\}
\end{equation*}
The \textbf{restriction} of $F$ to $A$ is the set
\begin{equation*}
F\restriction A=\{\langle u,v\rangle\mid uFv\land u\in A\}
\end{equation*}
The \textbf{image} of $A$ \textbf{under} $F$ is the set
\begin{align*}
F[A]&=\{v\mid\exists u\in A(uFv)\}\\
&=\text{ran}(F\restriction A)
\end{align*}
\end{definition}
\noindent In each case we prove existence using the subset axioms.
\begin{proof}(Inverse)
We show 
\begin{equation*}
\forall F\exists D\forall x(x\in D\leftrightarrow\exists u\exists v(x=\langle u,v\rangle\land vFu))
\end{equation*}
First we show
\begin{equation*}
\forall F\forall x(\exists u\exists v(x=\langle u,v\rangle\land vFu)\to x\in\text{ran}F\times\text{dom}F)
\end{equation*}
Let $F$ and $x$ be arbitrary. Suppose there exists $u$ and $v$ such that $x=\langle u,v\rangle$ and $vFu$. Then $v\in\text{dom}F$ and $u\in\text{ran}F$, so since $x=\langle u,v\rangle$,
$x\in\text{ran}F\times\text{dom}F$.\\
\indent The subset axiom allows us to assert
\begin{equation*}
\forall F\exists D\forall x(x\in D\leftrightarrow x\in\text{ran}F\times\text{dom}F\land\exists u\exists v(x=\langle u,v\rangle\land vFu))
\end{equation*}
The desired result follows from these two facts. Uniqueness follows from extensionality.
\end{proof}
\noindent(next page)\newpage
\begin{proof}(Composition) We show
\begin{equation*}
\forall F\forall G\exists D\forall x(x\in D\leftrightarrow[\exists u\exists v(x=\langle u,v\rangle\land\exists t(uGt\land tFv))])
\end{equation*}
We first show
\begin{equation*}
\forall F\forall G\forall x([\exists u\exists v(x=\langle u,v\rangle\land\exists t(uGt\land tFv))]\to x\in\text{dom}G\times\text{ran}F)
\end{equation*}
Let $F,G,$ and $x$ be arbitrary. Suppose there exists $u$ and $v$ such that $x=\langle u,v\rangle$ and $\exists t(uGt\land tFv)$. Then there exists $t$ such that $uGt$ and $tFv$; this means that
$u\in\text{dom}G$ and $v\in\text{ran}F$. So since $x=\langle u,v\rangle$, $x\in\text{dom}G\times\text{ran}F$.\\
\indent The subset axiom allows us to assert
\begin{equation*}
\forall F\forall G\exists D\forall x(x\in D\leftrightarrow x\in\text{dom}G\times\text{ran}F\land[\exists u\exists v(x=\langle u,v\rangle\land\exists t(uGt\land tFv))])
\end{equation*}
The desired result follows from these two facts. Uniqueness follows from extensionality.
\end{proof}
\begin{proof}(Restriction) We show
\begin{equation*}
\forall F\forall A\exists D(\forall x(x\in D\leftrightarrow\exists u\exists v(x=\langle u,v\rangle\land uFv\land u\in A)))
\end{equation*}
It is straightforward to show
\begin{equation*}
\forall F\forall A\forall x(\exists u\exists v(x=\langle u,v\rangle\land uFv\land u\in A)\to x\in F)
\end{equation*}
Then with the subset axiom we can assert
\begin{equation*}
\forall F\forall A\exists D(\forall x(x\in D\leftrightarrow x\in F\land\exists u\exists v(x=\langle u,v\rangle\land uFv\land u\in A)))
\end{equation*}
The desired result follows from these two facts. Uniqueness follows from extensionality.
\end{proof}
\begin{proof}(Image)
We show 
\begin{equation*}
\forall F\forall A\exists D\forall x(x\in D\leftrightarrow\exists u\in A(uFx))
\end{equation*}
It is straightforward to show
\begin{equation*}
\forall F\forall A\forall x(\exists u\in A(uFx)\to x\in\text{ran}F)
\end{equation*}
Then with the subset axiom we can assert
\begin{equation*}
\forall F\forall A\exists D\forall x(x\in D\leftrightarrow x\in\text{ran}F\land\exists u\in A(uFx))
\end{equation*}
The desired result follows from these two facts. Uniqueness follows from extensionality.\\
(next page)\newpage
Next we show $F[A]=\text{ran}(F\restriction A)$. Let $x$ be arbitrary.\\
\indent($\rightarrow$) Suppose $x\in F[A]$. This means $\exists u\in A(uFx)$, so there exists some $u\in A$ such that $uFx$. So $\langle u,x\rangle\in F\restriction A$ and 
$x\in\text{ran}(F\restriction A)$.\\
\indent($\leftarrow$) Now suppose $x\in\text{ran}(F\restriction A)$. Then there exists some $t$ such that $\langle t,x\rangle\in F\restriction A$. This means 
$tFx$ and $t\in A$, so $x\in F[A]$.
\end{proof}

\subsection{Theorems}
\begin{theorem}\label{theorems0}
For a set $F$, dom$\,F^{-1}=\text{ran}\,F$ and ran$\,F^{-1}=\text{dom}\,F$. For a relation $F$, $(F^{-1})^{-1}=F$.
\end{theorem}
\begin{proof}
First to show that for any arbitrary set $F$, dom$F^{-1}=\text{ran}F$. Let $x$ be arbitrary and suppose $x\in\text{dom}F^{-1}$. Then there exists some $y$ such that $xF^{-1}y$. By definition
this means $yFx$, so $x\in\text{ran}F$. Now suppose $x\in\text{ran}F$. Then there exists some $y$ such that $yFx$. By definition this means $xF^{-1}y$, so $x\in\text{dom}F^{-1}$.\\
\indent Next we show that for any arbitrary set $F$, ran$F^{-1}=\text{dom}F$. Let $x$ be arbitrary and suppose $x\in\text{ran}F^{-1}$. Then there exists some $y$ such that $yF^{-1}x$. 
By definition this means $xFy$, so $x\in\text{dom}F$. Now suppose $x\in\text{dom}F$. Then there exists some $y$ such that $xFy$. By definition then $yF^{-1}x$, so $x\in\text{ran}F^{-1}$.\\
\indent Finally we show that for any arbitrary relation $F$, $(F^{-1})^{-1}=F$. Let $x$ be arbitrary and suppose $x\in(F^{-1})^{-1}$. Then there exists $u$ and $v$ such that $x=\langle u,v\rangle$
and $vF^{-1}u$. By definition we then have $uFv$ and $x=\langle u,v\rangle\in F$. Now suppose $x\in F$. Since $F$ is a relation $x$ must be an ordered pair, whose first and second coordinates 
can be denoted as $u$ and $v$ such that $x=\langle u,v\rangle$ and $uFv$. By definition $vF^{-1}u$ and $u(F^{-1})^{-1}v$, so $x=\langle u,v\rangle\in(F^{-1})^{-1}$.
\end{proof}
\begin{theorem}\label{theorems3}
For a set $F$, $F^{-1}$ is a function iff $F$ is single-rooted. A relation $F$ is a function iff $F^{-1}$ is single-rooted.
\end{theorem}
\begin{proof}
First we prove that for any set $F$, $F^{-1}$ is a function iff $F$ is single-rooted.\\
\indent($\rightarrow$)
First suppose $F^{-1}$ is a function. Let $y$ be some element of ran$F$. By definition there exists some $x$ such that $xFy$. We also have $yF^{-1}x$ and $y\in\text{dom}F^{-1}$.
Now let there be some other $x'$ such that $x'Fy$.
Then since $xFy$ and $x'Fy$, $yF^{-1}x$ and $yF^{-1}x'$. Since $F^{-1}$ is a function we then have $x'=x$, so $F$ is single-rooted.\\
\indent($\leftarrow$) Now suppose $F$ is single-rooted. Let $y$ be some element of dom$F^{-1}$. By definition this means there exists some $x$ such that
$yF^{-1}x$, and $xFy$. So $y\in\text{ran}F$. Let $x_1$ and $x_2$ exist such that $yF^{-1}x_1$ and $yF^{-1}x_2$, meaning $x_1Fy$ and $x_2Fy$. Since $F$ is single rooted, we must
then have $x_1=x_2$. So $F^{-1}$ is a function.\\
(next page)\newpage
Now we prove that a relation $F$ is a function iff $F^{-1}$ is single-rooted.\\
\indent($\rightarrow$) Suppose $F$ were a function. Let $x$ be an element of ran$F^{-1}$.
By definition there then exists some $y$ such that $yF^{-1}x$. This also means $xFy$ so $x\in\text{dom}F$. Let $y_1$ and $y_2$ be arbitrary such that $y_1F^{-1}x$ and $y_2F^{-1}x$. Then $xFy_1$
and $xFy_2$. Since $F$ is a function we then have $y_1=y_2$.\\
\indent($\leftarrow$) Suppose $F^{-1}$ were single-rooted. Let $x$ be an element of dom$F$. Then by definition there exists some $y$ such that $xFy$. This means $yF^{-1}x$ so $x\in\text{ran}F^{-1}$.
Now let $y_1$ and $y_2$ be arbitrary such that $xFy_1$ and $xFy_2$. This means $y_1F^{-1}x$ and $y_2F^{-1}x$; since $F^{-1}$ is single-rooted, $y_1=y_2$.
\end{proof}
\begin{theorem}\label{theorems1}
Assume that $F$ is a one-to-one function. If $x\in\text{dom}F$, then $F^{-1}(F(x))=x$. If $y\in\text{ran}F$, then $F(F^{-1}(y))=y$.
\end{theorem}
\begin{proof}
First to show $\forall x(x\in\text{dom}F\to F^{-1}(F(x))=x)$. Let $x$ be arbitrary and suppose $x\in\text{dom}F$. Then there exists some $y$ such that $\langle x,y\rangle\in F$; by definition
this $y$ is unique and $y=F(x)$. By definition $\langle y,x\rangle\in F^{-1}$. Since $F$ is one-to-one $F^{-1}$ is a function and $x=F^{-1}(y)=F^{-1}(F(x))$.\\
\indent Now to show $\forall y(y\in\text{ran}F\to F(F^{-1}(y))=y)$. Let $y$ be arbitrary and suppose $y\in\text{ran}F$. Then by definition there exists a unique $x$ such that 
$\langle x,y\rangle\in F$, and $y=F(x)$. We also have $\langle y,x\rangle\in F^{-1}$; since $F^{-1}$ is a function $x=F^{-1}(y)$. So $y=F(x)=F(F^{-1}(y))$.
\end{proof}
\begin{theorem}\label{theorems2}
Assume $F$ and $G$ are functions. Then $F\circ G$ is a function. Its domain is
\begin{equation*}
\{x\in\text{dom}G\mid G(x)\in\text{dom}F\}
\end{equation*}
and for $x$ in its domain $(F\circ G)(x)=F(G(x))$.
\end{theorem}
\begin{proof}
Assuming $F$ and $G$ are functions. First we show that $F\circ G$ is a function.
Suppose $x\in\text{dom}(F\circ G)$. Then by definition there exists $y$ such that $\langle x,y\rangle\in F\circ G$. Suppose $y_1$ and $y_2$ are arbitrary elements such that
$\langle x,y_1\rangle\in F\circ G$ and $\langle x,y_2\rangle\in F\circ G$; then by definition there exists $t_1$ and $t_2$ such that $\langle x,t_1\rangle\in G$,
$\langle t_1,y_1\rangle\in F$, $\langle x,t_2\rangle\in G$, and $\langle t_2,y_2\rangle\in F$.
Since $G$ is a function we then have $t_1=t_2$. So 
$\langle t_1,y_1\rangle\in F$ and $\langle t_1,y_2\rangle\in F$. Since $F$ is a function we then have $y_1=y_2$.\\
\indent Now we show dom$(F\circ G)=\{x\in\text{dom}G\mid G(x)\in\text{dom}F\}$. We can assert the existence of the right side by the subset axiom:
\begin{equation*}
\exists D(\forall x(x\in D\leftrightarrow x\in\text{dom}G\land G(x)\in\text{dom}F))
\end{equation*}
$G(x)$ exists since $G$ is a function and dom$G$ and dom$F$ are sets.\\
\indent($\rightarrow$) Suppose $x\in\text{dom}(F\circ G)$. Then by definition there exists $y$ such that $\langle x,y\rangle\in F\circ G$; then there exists $t$ such that $\langle x,t\rangle\in G$
and $\langle t,y\rangle\in F$. Then $x\in\text{dom}G$ and since $G$ is a function $G(x)=t\in\text{dom}F$.\\
\indent($\leftarrow$) Suppose now $x\in\{x\in\text{dom}G\mid G(x)\in\text{dom}F\}$. Then $x\in\text{dom}G$ and $G(x)\in\text{dom}F$. The former means there exists $t$ such that $xGt$, so $t=G(x)$.
This, combined with the latter means $t\in\text{dom}F$, so there exists $y$ such that $tFy$.
By definition we then have $\langle x,y\rangle\in F\circ G$ and $x\in\text{dom}(F\circ G)$.\\
(next page)\newpage
Finally we show that $\forall x\in\text{dom}(F\circ G)[(F\circ G)(x)=F(G(x))]$. Let $x$ be an arbitrary element of dom$(F\circ G)$. Then there exists $y$ such that $\langle x,y\rangle\in F\circ G$
Since $F\circ G$ is a function $y=(F\circ G)(x)$. By definition there exists $t$ such that
$xGt$ and $tFy$. Since $G$ is a function $t=G(x)$ and $y=F(t)$.
Putting it all together we have $(F\circ G)(x)=y=F(t)=F(G(x))$.
\end{proof}

\subsection{Identity relation}
\begin{definition}
For a set $\omega$, the identity function on $\omega$ is 
\begin{equation*}
I_\omega=\{\langle n,n\rangle\mid n\in\omega\}
\end{equation*}
\end{definition}
\begin{proof}(Existence)
We want to show
\begin{equation*}
\forall\omega\exists D(\forall x(x\in D\leftrightarrow\exists n\in\omega(x=\langle n,n\rangle)))
\end{equation*}
First we show
\begin{equation*}
\forall\omega\forall x(\exists n\in\omega(x=\langle n,n\rangle)\to x\in\omega\times\omega)
\end{equation*}
Let $\omega$ and $x$ be arbitrary. Suppose there exists some $n\in\omega$ such that $x=\langle n,n\rangle$. Then by definition $x\in\omega\times\omega$. 
By the subset axiom we can assert
\begin{equation*}
\forall\omega\exists D(\forall x(x\in D\leftrightarrow x\in\omega\times\omega\land\exists n\in\omega(x=\langle n,n\rangle)))
\end{equation*}
where the desired conclusion follows from these two facts. Uniqueness follows from extensionality.
\end{proof}
\begin{proof}($I_\omega$ is a function on $\omega$) We first show that $I_\omega$ is a function.
Let $x\in\text{dom}I_\omega$. Then by definition there exists $y$ such that $\langle x,y\rangle\in I_\omega$. Let $y_1$ and $y_2$ be arbitrary such that 
$\langle x,y_1\rangle\in I_\omega$ and $\langle x,y_2\rangle\in I_\omega$. Then there exists $n_1$ and $n_2$ such that 
$\langle x,y_1\rangle=\langle n_1,n_1\rangle$ and $\langle x,y_2\rangle=\langle n_2,n_2\rangle$.
So $n_1=x=n_2$ and $y_1=n_1=n_2=y_2$.\\
\indent Next we show $\text{dom}I_\omega=\omega$. Let $x\in\text{dom}I_\omega$. Then there exists some $y$ such that $\langle x,y\rangle\in I_\omega$. By definition there exists some $n\in\omega$
such that $\langle x,y\rangle=\langle n,n\rangle$. So $x=n\in\omega$. Now let $x\in\omega$. By the pairing axiom $\langle x,x\rangle$ exists and by definition is an element of $I_\omega$. 
So $x\in\text{dom}I_\omega$.\\
\indent Finally we show $\text{ran}I_\omega=\omega$. Let $x\in\text{ran}I_\omega$. Then there exists $y$ such that $\langle y,x\rangle\in I_\omega$. By definition there then
exists $n\in\omega$ such that $\langle n,n\rangle=\langle y,x\rangle$, and $x=n\in\omega$. Now let $x\in\omega$; then $\langle x,x\rangle$ exists and by definition is an element of $I_\omega$.
So $x\in\text{ran}I_\omega$.
\end{proof}
\newpage

\subsection{More theorems}
\begin{theorem}
Assuming that $G$ is some one-to-one function, $G^{-1}\circ G$ is the identity function on dom$G$, $I_{\text{dom}G}$,
and $G\circ G^{-1}$ is the identity on ran$G$, $I_{\text{ran}G}$.
\end{theorem}
\begin{proof}
Assuming that $G$ is some one-to-one function, we first show $G^{-1}\circ G$ is the identity function on dom$G$, $I_{\text{dom}G}$. Since $G$ is a one-to-one function, by theorem \ref{theorems3} 
$G^{-1}$ is also a one-to-one function; 
by theorem \ref{theorems2} $G^{-1}\circ G$ is a function.\\
\indent We can show that $\text{dom}(G^{-1}\circ G)=\text{dom}G$. By theorem \ref{theorems2}, the domain of $G^{-1}\circ G$ is given by
\begin{equation*}
\{x\in\text{dom}G\mid G(x)\in\text{dom}G^{-1}\}
\end{equation*}
Suppose $x\in\text{dom}(G^{-1}\circ G)$. Then by the above equivalence it immediately follows that $x\in\text{dom}G$. Now suppose $x\in\text{dom}G$. 
Then there exists some $y$ such that $xGy$ and $yG^{-1}x$. This means $G(x)=y\in\text{dom}G^{-1}$. By the above equivalence 
$x\in\{x\in\text{dom}G\mid G(x)\in\text{dom}G^{-1}\}=\text{dom}(G^{-1}\circ G)$.\\
\indent Now to show $G^{-1}\circ G=I_{\text{dom}G}$. Let $\langle x,y\rangle$ be an arbitrary element of $G^{-1}\circ G$. Then $x\in\text{dom}(G^{-1}\circ G)=\text{dom}G$. By theorem \ref{theorems2}
$(G^{-1}\circ G)(x)=G^{-1}(G(x))$. By theorem \ref{theorems1} $G^{-1}(G(x))=x$.
Putting it all together we have $y=(G^{-1}\circ G)(x)=G^{-1}(G(x))=x$, so $\langle x,y\rangle=\langle x,x\rangle$ for $x\in\text{dom}G$, so by definition $\langle x,y\rangle\in I_{\text{dom}G}$.\\
\indent Now suppose $\langle x,y\rangle\in I_{\text{dom}G}$. Then there exists some $n\in\text{dom}G$ such that $\langle x,y\rangle=\langle n,n\rangle$. 
This implies $x=n=y$ and $x\in\text{dom}G=\text{dom}(G^{-1}\circ G)$ in a manner similar to the previous direction $(G^{-1}\circ G)(x)=G^{-1}(G(x))=x=y$. So $\langle x,y\rangle\in G^{-1}\circ G$.\\
\indent Next we show $G\circ G^{-1}$ is the identity on ran$G$, $I_{\text{ran}G}$. First we show 
that $\text{dom}(G\circ G^{-1})=\text{ran}G$. By theorem \ref{theorems2} $G\circ G^{-1}$ is a function and the domain of $G\circ G^{-1}$ is equivalent to
\begin{equation*}
\{x\in\text{dom}G^{-1}\mid G^{-1}(x)\in\text{dom}G\}
\end{equation*}
Suppose $x\in\text{dom}(G\circ G^{-1})$. Then by the above equivalence and theorem \ref{theorems0} we immediately have $x\in\text{dom}G^{-1}=\text{ran}G$. Now suppose $x\in\text{ran}G$. 
Then $x\in\text{dom}G^{-1}$ and there exists
some $y$ such that $yGx$ and $xG^{-1}y$. So $G^{-1}(x)=y\in\text{dom}G$. By the above equivalence
we then have $x\in\text{dom}(G\circ G^{-1})$.\\
\indent Suppose $\langle x,y\rangle\in G\circ G^{-1}$. Then $x\in\text{dom}(G\circ G^{-1})=\text{ran}G$. By theorem \ref{theorems2} we have $y=(G\circ G^{-1})(x)=G(G^{-1}(x))$. 
Since $G$ is a one-to-one function and $x\in\text{ran}G$, by theorem \ref{theorems1} $G(G^{-1}(x))=x$. Putting it all together we have $y=(G\circ G^{-1})(x)=G(G^{-1}(x))=x$. 
So $\langle x,y\rangle=\langle x,x\rangle$ for $x\in\text{ran}G$. By definition we have
$\langle x,y\rangle\in I_{\text{ran}G}$.\\
\indent Now suppose $\langle x,y\rangle\in I_{\text{ran}G}$. By definition there exists some $n\in\text{ran}G$ such that $\langle x,y\rangle=\langle n,n\rangle$.
This implies $x=n=y$ and $x\in\text{ran}G=\text{dom}(G\circ G^{-1})$.
Then in a manner similar to the previous direction, $(G\circ G^{-1})(x)=G(G^{-1}(x))=x=y$. So
$\langle x,y\rangle\in G\circ G^{-1}$.
\end{proof}
\noindent(next page)\newpage
\begin{theorem}
For any sets $F$ and $G$,
\begin{equation*}
(F\circ G)^{-1}=G^{-1}\circ F^{-1}
\end{equation*}
\end{theorem}
\begin{proof}
Both $(F\circ G)^{-1}$ and $G^{-1}\circ F^{-1}$ are, by definition, relations. We have the string of equivalences for arbitrary
$\langle x,y\rangle$.
\begin{align*}
\langle x,y\rangle\in(F\circ G)^{-1}&\leftrightarrow\langle y,x\rangle\in F\circ G\\
&\leftrightarrow\exists t(yGt\land tFx)\\
&\leftrightarrow\exists t(xF^{-1}t\land tG^{-1}y)\\
&\leftrightarrow\langle x,y\rangle\in G^{-1}\circ F^{-1}\qedhere
\end{align*}
\end{proof}
\begin{theorem}
Assume that $F:A\to B$, and that $A$ is nonempty.
\begin{enumerate}
\item There exists a function $G:B\to A$ (a ``left inverse'') such that $G\circ F$ is the identity function $I_A$ on $A$ iff $F$ is one-to-one.
\item There exists a function $H:B\to A$ (a ``right inverse'') such that $F\circ H$ is the identity function $I_B$ on $B$ iff $F$ is maps $A$ onto $B$.
\end{enumerate}
\end{theorem}
\begin{proof}(1.)\\
\indent$(\rightarrow)$ Suppose there exists some $G:B\to A$ such that $G\circ F$ is the identity function $I_A$ on $A$. Let $y$ be an element of ran$F$.
Then by definition there exists $x$ such that $xFy$. Now let $x'$ be arbitrary such that $x'Fy$.
We know that $y\in\text{ran}F\subseteq B=\text{dom}G$. By theorem \ref{theorems2} $x\in\text{dom}(G\circ F)$ and $G(y)=G(F(x))=(G\circ F)(x)$ since 
$G\circ F$ is the identity function $I_A$ we then have $(G\circ F)(x)=x$. A similar argument 
shows $G(y)=G(F(x'))=(G\circ F)(x')=x'$. So $yGx'$ and $yGx$; since $G$ is a function $x'=x$.\\
\indent $(\leftarrow)$ Suppose now that $F$ is one-to-one. We need to come up with some function $G$ that satisfies the following requirements: $G$ is a function, dom$G=B$, ran$G\subseteq A$, and 
$G\circ F=I_A$. Since $F$ is one-to-one $F^{-1}$ is a function from $\text{ran}F$ onto $A$. By assumption $A$ is nonempty, so we can fix some $a$ in $A$, defining $G$ such that it assigns $a$ to 
every point in $B-\text{ran}F$ (so that the domain of $G$ encompasses all of $B$):
\begin{equation*}
G(x)=\begin{cases}
F^{-1}(x)&\text{if }x\in\text{ran}F\\
a&\text{if }x\in B-\text{ran}F
\end{cases}
\end{equation*}
More precisely, our candidate function is
\begin{equation*}
G=F^{-1}\cup(B-\text{ran}F)\times\{a\}
\end{equation*}
(next page)\newpage
We show that $G$, defined as
\begin{equation*}
G=F^{-1}\cup(B-\text{ran}F)\times\{a\}
\end{equation*}
is, firstly, a function. Let $x$ be an arbitrary element of dom$G$. By definition then exists $y$ such that $xGy$. Now let $y'$ be arbitrary such that $xGy'$.
We have four cases.\\
\indent Case 1: $\langle x,y\rangle\in F^{-1}$, $\langle x,y'\rangle\in F^{-1}$. Then since $F^{-1}$ is a function, $y=y'$.\\
\indent Case 2: $\langle x,y\rangle\in F^{-1}$, $\langle x,y'\rangle\in(B-\text{ran}F)\times\{a\}$.
In this case $x\in(B-\text{ran}F)$ so $x\notin\text{ran}F$. But since $\langle x,y\rangle\in F^{-1}$ we also have $\langle y,x\rangle\in F$ and $x\in\text{ran}F$. 
This case leads to a contradiction and cannot occur; it is excluded.\\
\indent Case 3: $\langle x,y\rangle\in(B-\text{ran}F)\times\{a\}$, $\langle x,y'\rangle\in F^{-1}$.
In a manner similar to case 2, this case leads to a contradiction and can be excluded.\\
\indent Case 4: $\langle x,y\rangle\in(B-\text{ran}F)\times\{a\}$, $\langle x,y'\rangle\in(B-\text{ran}F)\times\{a\}$. Then $y=a=y'$.\\
\indent Next we show dom$G=B$. First suppose $x\in\text{dom}G$. Then there exists $y$ such that $\langle x,y\rangle\in G$, meaning $\langle x,y\rangle\in F^{-1}$ or 
$\langle x,y\rangle\in(B-\text{ran}F)\times\{a\}$. In the first case $\langle y,x\rangle\in F$ so
$x\in\text{ran}F\subseteq B$ and $x\in B$. In the second case it immediately follows that $x\in B$.\\
\indent Now suppose $x\in B$. We have two cases. First suppose $x\in\text{ran}F$. Then there exists $y$ such that $xF^{-1}y$; so $xGy$ and $x\in\text{dom}G$. Next suppose $x\notin\text{ran}F$.
Then it immediately follows that $x\in B-\text{ran}F$; $\langle x,a\rangle$ exists by the pairing axiom and is a member of $(B-\text{ran}F)\times\{a\}$, so 
$\langle x,a\rangle\in G$ and $x\in\text{dom}G$.\\
\indent Next we show ran$G\subseteq A$. Suppose $x\in\text{ran}G$. Then there exists $y$ such that
$\langle y,x\rangle\in F^{-1}$ or $\langle y,x\rangle\in(B-\text{ran}F)\times\{a\}$. In the first case $\langle x,y\rangle\in F$ and $x\in\text{dom}F$. In the second case it immediately follows
that $x=a\in A$.\\
\indent Finally we show $G\circ F=I_A$. Both $G\circ F$ and $I_A$ are relations. Suppose $\langle x,y\rangle$ is an arbitrary element of $G\circ F$. Then there exists $t$ such that $xFt$ and $tGy$.
The latter implies $\langle t,y\rangle\in F^{-1}$ or $\langle t,y\rangle\in(B-\text{ran}F)\times\{a\}$. In the first case $yFt$ and $xFt$; so since $F$ is one-to-one $x=y$. 
Since $\langle x,y\rangle=\langle x,x\rangle$ for $x\in\text{dom}F=A$, by definition $\langle x,y\rangle\in I_A$. In the other case where 
$\langle t,y\rangle\in(B-\text{ran}F)\times\{a\}$ we have $t\notin\text{ran}F$. But since $xFt$ we also have $t\in\text{ran}F$. This case leads to a contradiction and can be excluded.\\
\indent Suppose now that $\langle x,y\rangle$ is an arbitrary element of $I_A$. Then there exists some $z\in A$ such that 
$\langle x,y\rangle=\langle z,z\rangle$. Since $A=\text{dom}F$, there exists $z_0$ such that $zFz_0$; it follows that $z_0\in\text{ran}F\subseteq B$ and $z_0\in B=\text{dom}G$. 
Then since $G$ was proven to be a function there exists $z_1$ such that $z_0Gz_1$. We have 
$\langle z_0,z_1\rangle\in F^{-1}$ or $\langle z_0,z_1\rangle\in (B-\text{ran}F)\times\{a\}$
since $z_0\in\text{ran}F$ the latter case is false and $\langle z_0,z_1\rangle\in F^{-1}$.
We then have $zFz_0$ and $z_1Fz_0$; since $F$ is one-to-one, $z_1=z$. 
So since $zFz_0$ and $z_0Gz_1\leftrightarrow z_0Gz$, 
$\langle x,y\rangle=\langle z,z\rangle\in G\circ F$.
\end{proof}
\noindent(next page)\newpage
\begin{proof}(2)\\
\indent($\rightarrow$)



\end{proof}










\end{document}
